%! ~~~ Packages Setup ~~~ 
\documentclass[]{article}
\usepackage{lipsum}

% Design
\usepackage[left=1.2in, right=1.2in, top=0.5in, bottom=0in]{geometry}
\usepackage{multicol}
\usepackage[skip=4pt, indent=0pt]{parskip}
\usepackage[normalem]{ulem}

\renewcommand\labelitemi{$\bullet$}
\usepackage{titlesec}
\titleformat{\section}[block]
{\fontsize{20}{40}}
{\large\dotfill \Large(\thesection)\large \dotfill}
{0em}
{\vspace{2pt} \newline \hfil \large \filleft \filright \MakeUppercase}
\usepackage{graphicx}
\graphicspath{ {./} }

\usepackage[colorlinks]{hyperref}
\usepackage{yfonts}
\def\gothstart#1{\noindent\smash{\lower3ex\hbox{\llap{\Huge\gothfamily#1}}}
    \parshape=3 3.1em \dimexpr\hsize-3.4em 3.4em \dimexpr\hsize-3.4em 0pt \hsize}
\def\frakstart#1{\noindent\smash{\lower3ex\hbox{\llap{\Huge\frakfamily#1}}}
    \parshape=3 1.5em \dimexpr\hsize-1.5em 2em \dimexpr\hsize-2em 0pt \hsize}
\pagenumbering{gobble}


% Language Shortcuts
\newcommand\del   {$ \!\! $}

\newcommand{\rn}[1]{
    \textup{\uppercase\expandafter{\romannumeral#1}}\textit{}
}

\makeatletter
\newcommand{\skipitems}[1]{
    \addtocounter{\@enumctr}{#1}
}
\makeatother
\usepackage{scalefnt}

\makeatletter
\def\columnseprulecolor\vrule\@width\columnseprule{%
    \vbox to \ht\mult@rightbox{\leaders\vbox{\kern2pt\hbox{.}\kern2pt}\vfill}}
\makeatother
\setlength{\columnsep}{1cm}
\setlength{\multicolsep}{0pt}% 50% of original values

%! ~~~ Document ~~~

\author{{Shahar Perets}}
\title{English Book Report $\sim$ One-Pager}
\begin{document}
    \,
    \vfil
    \hfil \fontsize{24.88}{10}{\swabfamily The End of Eternity}{\!\bf \Large/}{\large Isaac Asimov}
    \\ \,
    \normalsize
    
    \begin{center}
           \textit{I tried to make that as clear as possible without being too long, but sometimes I'll use terms that I haven't defined}
    \end{center}
    \begin{multicols}{2}
        \section{Could the story take place as it is on a deserted island?}
        {\sf The story requires many people from different centuries, that don't know each other, to be possible. In addition, the Eternity itself is a completely different thing than the regular time field; hence, it could not exist together with the regular reality on a deserted island. Lastly, other intelligent species and empires in the universe are taken into consideration near the end of the book -- this could have not coexisted together with humanity without interacting, nor be an empire in the first place, without knowing each other on a deserted island. 
            
            The point of many parts of the book is that they are unbounded with the time and place, and limiting the story to a specific place limits portions of the book, and effectively defeats its goal. }
        
        \vfill\null
        \columnbreak
        
        \section{My favorite part of the story}
        {\sf My favorite part of the book is the ending. In a complete contrast the rest of the book. In the ending, two things come to their pick: First of all, Asimov deals with many paradoxes, and presents the idea of using the energy at the end of Eternity to use the Eternity to come back to before it even existed, and recreate the Eternity there -- which creates a time loop (so that the Eternity created itself and will always exist). Secondly, concerns about the weak pace of humanity's development are raised, since all of the ``fixes'' made in time cause things like nuclear power and other discoveries the be delayed. That way, the whole moral behind the Eternity which was taken for granted up to this point, is being questioned. Together with those paradoxes, I think that the ending is mind-boggling and the most interesting to read. }
        \vfill\null
        \end{multicols}
        \begin{multicols}{2}
        \section{The character that I most identify with}
        {\sf I most identify with N\"oys. She conveys the perfectly rational, beautiful, and impossibly self-tuned woman that could exist. She has full control over her body and expression, and she knows clearly the reason for her actions. N\"oys is able to completely fool Harlan and use him to cause the end of Eternity and liberate humanity from the constant changes that the technicians make to minimize human suffering (but in the long run, results in humanity being weakened and not innovative, and decline till ending in the shadow of other species).}
        \vfill\null 
        
        \columnbreak 
        \section{How would I solve the main conflict?}
        {\sf There are several conflicts in the book. The one that escorts most of the plot, is Harlan's conflict that he thought he had with the other Eternals over him breaking the rules, interacting with N'oys and even bringing her into the Eternity. I think that I wouldn't have brought her into Eternity in the first place, yet if I came to a point at which I did bring her into Eternity, I would probably act the same as he did.: threatening others and doing everything to get her back of the kettle block (times above the year 10 million, where the Eternity mistrustfully is inaccessible). }
        \vfill\null
    \end{multicols}
    \dotfill
     \vspace{2pt} \newline \hfil \large \filleft \filright \fontsize{20}{40} RECOMMENDATION
    
    \normalsize
    {\sf I recommend this book. Asimov is able to ``play'' and change how reality and time works in the book, and to change our prespective on those. I touches deep moral questions and issues. The book is interesting and has a decent opening yet keeps on fast face of development. I think that anyway has something to take and learn from it. }
    
    \dotfill
    
\end{document}