%! ~~~ Packages Setup ~~~ 
\documentclass[]{article}
\usepackage{lipsum}
\usepackage{rotating}


% Math packages
\usepackage[usenames]{color}
\usepackage{forest}
\usepackage{ifxetex,ifluatex,amssymb,amsmath,mathrsfs,amsthm,witharrows,mathtools,mathdots}
\usepackage{amsmath}
\WithArrowsOptions{displaystyle}
\renewcommand{\qedsymbol}{$\blacksquare$} % end proofs with \blacksquare. Overwrites the defualts. 
\usepackage{cancel,bm}
\usepackage[thinc]{esdiff}

% Deisgn
\usepackage[labelfont=bf]{caption}
\usepackage[margin=1.4in]{geometry}
\usepackage{multicol}
\usepackage[skip=7pt, indent=0pt]{parskip}
\usepackage[normalem]{ulem}
\forestset{default}
\renewcommand\labelitemi{$\bullet$}
\usepackage{titlesec}
\titleformat{\section}[block]
{\fontsize{15}{15}}
{\dotfill (\thesection)\dotfill}
{0em}
{\MakeUppercase}
\usepackage{graphicx}
\graphicspath{ {./} }

\usepackage[colorlinks]{hyperref}
\definecolor{mgreen}{RGB}{25, 160, 50}
\definecolor{mblue}{RGB}{30, 60, 200}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	citecolor=mgreen,
	linkcolor=black,
	urlcolor=mblue,
	pdftitle={AI Something}
}

\usepackage{yfonts}
\usepackage{wrapfig}
\def\pstart#1{\noindent\smash{\lower3ex\hbox{\llap{\Huge\gothfamily#1}}}
    \parshape=3 3.1em \dimexpr\hsize-3.4em 3.4em \dimexpr\hsize-3.4em 0pt \hsize}

%! ~~~ Document ~~~

\author{Shahar Perets}
\title{Post Reading $\sim$ {\huge \frakfamily Fahrenheit 451} $\sim$ Continue ``Fahrenheit''}
\date{May 5, 2025}
\begin{document}
	\maketitle
	
    \small \textit{Note: I changed the part from the original book, where they come back to the city, because it doesn't make sense and the radioactive radiation will kill them in a few hours, as it was in Hiroshima \& Nagasaki: more people died from the radiation than from heat and destruction. }
    
    \normalsize\pstart{The}\!\! Book People and Montag stand on the land, a week after the war. No food nor weapons were available to them since all of the nearby populated areas got bombed during the war, and they couldn't get any closer due to the dangerous radiation. Montag's shift was from the moment the sun was in the middle of the sky till the evening, so he had time to sleep. He couldn't wish himself a better group to be with -- some people read books about plants and knew what was edible and what not, and others were in the process of making small weapons and gunpowder (which turns out useful to scare animals even though they haven't had any guns) and some designed long-term plans using their knowledge from books like ``Robinson Crusoe'' and ``The Mysterious Island''. 
    
    Montag felt relatively useless during that time since the only book he remembered was ``Ecclesiastes''. He was exhausted from the physical work and many people knew him from his life as a fireman, and needless to say they didn't like him at first. With that said, they got used to him over time, after they met him close. And most importantly -- he was finally passionate about what he was doing. He \textit{wants} to rebuild society, to design the new world. To take a part in the reviving of the Phoenix. To finally have a goal in life. 
    
    The first few weeks were full in the continued search for food and supplies. It was relatively easy as a result of the bright summer and rich fields that were in this area. It was clear for all that the known world had destroyed itself -- if it wasn't the case, another military would have come to hold this place by now. After around 25 days, they stored enough food for the next several weeks. At that time Granger settled down in a talk to main goals -- the first was to store enough food and to find a safe place for the winter, and the second one was to take advantage of the summer to search for survivors. This was not an easy task; they needed to carefully avoid the radioactive arias, to avoid getting lost, and to come back until the sun came down. 
    
    There was a relatively common belief among the group that a small number of people among the book lovers that parts of the government were still hiding behind in the forest, safe from the fear of war. The logic behind this was that it can't be the case where every human being is being controlled -- someone also needs to control. With that said, there was no real evidence for that, and no one really knows if the ``elected'' prime minister is even actually a real person. 
    
    The day-to-day life wasn't that hard as it though it would be -- the experienced personal the good conditions helped them diffuse in the group and get used to the land. Every evening they would get together and sang poetry, that some have memorized -- anything from Yevgeny Yevtushenko's Babi Yar to Rückert's Kindertotenlieder. But for some reason that no one could describe or know, depression and anxiety was in the air. 
    
    But everything changed 2 months after they began searching. That time, Montag took part in a small searching group, led by Tom Paine. Around 2 kilometers northeast of the river, Byron lapsed on a metal pipe. They followed it and opened the shaft. They went down, thinking the place was abandoned. Suddenly, they heard a weak yelling, looked, and saw a thin person holding a gun on the side of the room, and taken apart bodies of men and women lying around. What happened was clear to all -- after all, some people left the city, which had a limited supply of food, and since they clearly ran out of food, they started eating each other. 
    
    Montag felt sorry for the people underground. He knew those people were the reason society destroyed itself, but he couldn't get himself to gloat for these, not even human anymore, creatures that starved there. He looked at them and thought that that's what not knowing anything resulted for them -- they didn't know how to even find food. The destruction of information that these creatures lead finally hit them. Luckily, he hadn't had to feel those feelings for so long -- they were pointing guns at him the rest of the unarmed group, which was quickly destroyed. 
    
    
    The rest of the book lovers never knew about this incident. They only knew they lost five people in the forest. And in some sense, it doesn't really matter at all; the Professors and Academics from the 20$^{\text{th}}$ century that the group was made of were all men. They were the last generation to live. The Phoenix was finally, after all of those years: \textit{dead}. \hfill $\blacksquare$
    
    \large \textbf{Statistics}\normalsize\dotfill
    
        {
            \hfil Word Count: 871
            \hfil Character Count: 4,892
            \hfil Sentences Count: 42
        }
        
        {
            \hfil Avg. Sentence Length: 20.7
            \hfil Avg. Word Length: 4.4
        }
	
	{\dotfill\\\vfil
		{\begin{center}{
					\textbf{Shahar Perets, \textit{2025}} \\
					\scriptsize Compiled With־ \LaTeX\ and Made Using Free Software
		}\end{center}}
	\vfil}
\end{document}